\documentclass[12pt, a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{geometry}
\usepackage[english]{babel}
\usepackage{url}
\usepackage{setspace}
\usepackage{hanging}
\renewcommand{\baselinestretch}{1.0}
\usepackage{multicol}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
%\newcommand{\tab}[1]{\hspace{.1\textwidth}\rlap{#1}}
\title{\textbf{Jothsna Rajan \\ \small{Updated: June 1, 2016} }}
\date{}
\geometry{a4paper, top = 25mm}
\usepackage{tabto}
\begin{document}
	\begin{center}
		\large{\textbf{Jothsna Rajan}} \\
		\small{Updated on: June 1, 2016}
	\end{center}
	\begin{multicols}{2}
		\begin{flushleft}
			\noindent Doctoral Student \\
			Centre for Public Policy \\
			Indian Institute of Management Bangalore \\
		\end{flushleft}
		\begin{flushright}
			\noindent jothsna.rajan14@iimb.ernet.in \\
			+91 9742462429 \\
			jothsnarajan@gmail.com \\
		\end{flushright}
	\end{multicols}
	\subsubsection*{EDUCATION}
	
	\noindent\textbf{Indian Institute of Management Bangalore} \\
	\textit{Fellow (PhD) Public Policy, 2014 onwards} \\
	
	\noindent\textbf{Indian Institute of Management Indore} \\
	\textit{Post Graduate Diploma in Management (MBA), 2008 - 10} \\
	Percentile of 99.70 in Common Admission Test (CAT) 2007 \\
	
	\noindent\textbf{College of Engineering Trivandrum} \\
	\textit{B.Tech Electrical Engineering, First Class, 2004 - 08}
	
	\subsubsection*{ACADEMIC APPOINTMENTS}
		\noindent\textbf{Rajagiri College of Social Sciences} \\
		Assistant Professor, Department of Business Studies, 2012 - 2014 
	\subsubsection*{CURRENT PROJECTS}
		\noindent \textit{Working paper} \\
		``Can Technology Overcome Social Disadvantage of School Children's Learning Outcomes? Evidence from a Large-Scale Experiment in India'' (with Gopal Naik, Chetan Chitre \& Manaswini Bhalla) \\ Available at SSRN: \url{http://ssrn.com/abstract=2775558} 
	\subsubsection*{ACCEPTED CONFERENCES} 
Dec 2015: \tabto{5em} ISI Delhi, Annual Conference on Economic Growth and Development \\
Jun 2016: \tabto{5em} UNU-WIDER, Conference on Human Capital and Growth, Helsinki \\
\tabto{5em} GREThA, Universit\'{e} de Bordeaux, 6th International Conference on \tabto{5em} Development Economics, Bordeaux \\	
\tabto{5em} University of Milan-Bicocca, International Association for Applied \\ \tabto{5em} Econometrics Annual Conference, Milan \\
Jul 2016: \tabto{5em} IIM Bangalore, Brown Bag series for Economics and Public Policy, \\
\tabto{5em} Bangalore \\
Aug 2016: \tabto{5em} The 69th European Meeting of the Econometric Society (ESEM), Geneva \\
\tabto{5em} The 2016 Asian Meeting of the Econometric Society (AMES2016),\\ 
\tabto{5em} Kyoto

	\subsubsection*{BOOK REVIEW}
	
	IIMB Management Review (forthcoming) \textit{Book Review: Leading Futures: Global Perspectives on Educational Leadership.} Edited by Alma Harris and Michelle S Jones
	
	\subsubsection*{TEACHING}
	\noindent\textbf{Graduate Program in Business Administration (2012-14)} \\
	\noindent\textit{Rajagiri College of Social Sciences} \\
	Operations Research, Project Management, Marketing Research, Business Update 
	\subsubsection*{RELATED COURSEWORK}
	\noindent\textbf{Indian Institute of Management, Bangalore (2014-16)} \\
	\noindent\textit{Public Policy} \\
	\\
	Political Economy of Development - Prof. Deepak Malghan, Public Policy Analysis - Prof. Deepak Malghan, Public Administration \& Law - Prof. Anil Suraj, Rural Banking \& Financial Inclusion- Prof. M S Sriram, Public Management - Prof. G Ramesh, Public Economics - Prof. Rajalaxmi Kamath, Psychological Perspectives in Public Policy - Prof. Ramadhar Singh, Topics in Applied Research - Prof. Shabana Mitra \\
	\\
	\noindent\textit{Research Methods} \\
	Inference in Observational Settings - Prof. Arnab Mukherji, Econometrics - Prof. Gopal Naik, Advanced Econometrics - Prof. Shailender Swaminathan, Research Methods- Prof. Gopal Naik, Qualitative Research Methods - Prof. Ganesh Prabhu
	\subsubsection*{PROFESSIONAL APPOINTMENTS}
	\noindent\textbf{IndeBo India Private Limited} \\
	Assistant Manager (Marketing), 2011 - 2012 
	\begin{itemize}
		\item Business Management and Development for the Western European market and further develop sales in new markets
		\item To develop and execute all round marketing campaigns encompassing web presence, brand building, \& product promotion
	\end{itemize}
	
	\noindent\textbf{Ballarpur Industries Limited} \\
	Assistant Manager (Product Management), 2010 - 2011
	\begin{itemize}
		\item Market Development and Product Development in the coated paper segment
		\item Studying the competitive landscape including competitor pricing and imports into the country
		\item Identify the profitable products in the portfolio in terms of contribution as well as market demand and liaise with the production as well as the sales team to achieve the contribution targets
	\end{itemize}
\end{document}